Data Preparation

### 2019-03-01 Data Preparation.Rmd
clean d_student

## Student Data
(In this section we use: `d_transcript`- contains the transcript information of students as was provided. It has 40 columns, and rows correspond roughly to a type of grade (e.g. final grade, attendance) per student per course per time they took it).

Our dataframe contains many variables and rows that are either empty or meaningless for our analysis. First, we filter, the final grades of studets to keep only relevant rows (Final Confirmed Grades are those with `Appraisal (Description)` as "Grade supervisor"). Then we select ony the 10 variables that we will use for the anlysis, and give them more comprehensible names.
```{r}
d_transcript <- d_transcript %>%

  # for simplicity, only keep courses of UCM program
  filter(
    `Program (Abbreviation)` == "7501",
    !str_detect(`Module (Abbrev.)`, "EXT")
    ) %>%

  # folowing guidelines of Richard Vos, we only consider: `Appraisal (Description)` == "Grade supervisor" and `Appraisal Type`          == "7055"
  filter(
    `Appraisal (Description)` == "Grade supervisor",
    `Appraisal Type`          == "7055" # removes ~ 15 observations
  ) %>%

  # Remove variables with only one value
  select_if(
    function(x) n_distinct(x) > 1
    ) %>%

  # Remove variables with more than 99% NA
  select_if(
    function(x) mean(is.na(x)) < 0.99
    ) %>%

@@

    Grade = case_when(
      is.na(Grade)  ~ "0",
      Grade == "NG" ~ "0",
      TRUE          ~ str_replace(
        Grade,
        pattern     = ",",
        replacement = "."
      )
    ) %>% 
      as.numeric

@@

  # if student took resit (recorder in same year and period), only keep failing grade
  # group_by(
  #   `Student ID`,
  #   `Course ID`,
  #   Year,
  #   Period
  #   ) %>%
  # summarize(
  #   Grade = min(Grade)
  #   ) %>%
  # ungroup %>%

@@

    time = paste(
      Year_numerical, substr(Period, 1, 1),
      sep = ""
      ),

    `Academic Year`= paste(
      Year_numerical, Year_numerical + 1,
      sep = "-")

    )
```

```{r}
print(d_transcript)
```

>>>>

## Student Data

* Is `Academic Work ID` a unique ID number?

* questions...

(In this section we use: `d_transcript`- contains the transcript information of students as was provided. It has 40 columns, and rows correspond roughly to a type of grade (e.g. final grade, attendance) per student per course per time they took it).

Our dataframe contains many variables and rows that are either empty or meaningless for our analysis. First, we filter, the final grades of studets to keep only relevant rows (Final Confirmed Grades are those with `Appraisal (Description)` as "Grade supervisor"). Then we select ony the 10 variables that we will use for the anlysis, and give them more comprehensible names.
```{r}
#
# Set up
UCM_course <- d_text$overview$`Course ID` %>%
  unique %>% 
  paste(collapse = "|")

# helper function
is_offered_at_UCM <- function(x) x %>% str_detect(UCM_course)

d_transcript <- d_transcript %>%

  # for simplicity, we only keep *UCM courses* taken in the framework of the *BA Liberal Arts and Sciences (UCM)* (7501)
  filter(
    `Module (Abbrev.)` %>% is_offered_at_UCM,
    `Program (Abbreviation)` == "7501"
  ) %>%

  # The dataset has multiple rows for each student - course following guidelines of Richard Vos, we only consider: `Appraisal (Description)` == "Grade supervisor" and `Appraisal Type` == "7055"
  filter(
    `Appraisal (Description)` == "Grade supervisor",
    `Appraisal Type`          == "7055" # removes ~ 15 observations
  ) %>%

  # Remove variables with only one value
  discard(
    function(x) n_distinct(x) == 1
  ) %>%

@@

    Grade = if_else(is.na(Grade) | Grade == "NG", "0", Grade) %>% str_replace(",", ".") %>% 
      as.numeric

@@

@@

    time = str_c(Year_numerical, substr(Period, 1, 1), sep = ""),

    `Academic Year`= str_c(Year_numerical, Year_numerical + 1, sep = "-")

  select(
    - Year_numerical,
    - Period
    ) %>%

  add_count(
    `Student ID`, `Course ID`, time,
    sort = TRUE
    ) %>%
  print

  # if student took resit (recorder in same year and period !!!NOT TRUE!!!), only keep failing grade 
  # group_by(
  #   `Student ID`,
  #   `Course ID`,
  #   Year,
  #   Period
  #   ) %>%
  # summarize(
  #   Grade = min(Grade)
  #   ) %>%
  # ungroup
```
